Using SIMD and SIMT vectorization to evaluate sparse chemical kinetic Jacobian matrices and thermochemical source terms

### 2018-06-13 paper.tex
add reference to OpenMP code

\Cref{F:dense_jac_scaling} shows scaling for the shallow-vectorized dense Jacobian OpenCL code.\todo{OpenCP and OpenMP?}{}
In this case, the isopentanol model scales the worst for both cases.
The sheer size of the dense isopentanol Jacobian limited the total number of states for the dense isopentanol Jacobian evaluation to \num{50000}---storing the dense matrix for a single thermochemical state takes over \SI{1}{\mega\byte} of data, so \num{50000} states requires over \SI{50}{\giga\byte} of memory); this greatly drops the computation cost for this case, and adversely affects the scaling efficiency as discussed in~\cref{S:source_results}.
Excluding the isopentanol model, the dense shallow-vectorized OpenCL code scales slightly better than for source-term evaluation: \numrange{0.70}{0.78} and \numrange{0.52}{0.61} for four and eight cores, respectively (compared with \numrange{0.66}{0.72} and \numrange{0.44}{0.48} for shallow-vectorized OpenCL source-term evaluations).
This results from the higher computational cost of Jacobian evaluation, and hence more available work per CPU core.
As in~\cref{S:source_results}, the shallow-vectorized dense Jacobian code running on \num{1} and \num{4} cores of the \avx/ machine performs roughly as fast as the OpenMP code on \num{4} and \num{16} cores, respectively.
The parallel scaling efficiency of OpenMP on \num{16} cores (excluding isopentanol) is \numrange{0.63}{0.71}, similar to the shallow vectorization's efficiency of \numrange{0.70}{0.78} for \num{4} cores.

>>>>

\Cref{F:dense_jac_scaling} shows scaling for the OpenMP and shallow-vectorized dense Jacobian OpenCL codes.
In this case, the isopentanol model scales the worst for both cases.
The sheer size of the dense isopentanol Jacobian limited the total number of states for the dense isopentanol Jacobian evaluation to \num{50000}---storing the dense matrix for a single thermochemical state takes over \SI{1}{\mega\byte} of data, so \num{50000} states requires over \SI{50}{\giga\byte} of memory); this greatly drops the computation cost for this case, and adversely affects the scaling efficiency as discussed in~\cref{S:source_results}.
Excluding the isopentanol model, the dense shallow-vectorized OpenCL code scales slightly better than for source-term evaluation: \numrange{0.70}{0.78} and \numrange{0.52}{0.61} for four and eight cores, respectively (compared with \numrange{0.66}{0.72} and \numrange{0.44}{0.48} for shallow-vectorized OpenCL source-term evaluations).
This results from the higher computational cost of Jacobian evaluation, and hence more available work per CPU core.
As in~\cref{S:source_results}, the shallow-vectorized dense Jacobian code running on \num{1} and \num{4} cores of the \avx/ machine performs roughly as fast as the OpenMP code on \num{4} and \num{16} cores, respectively.
The parallel scaling efficiency of OpenMP on \num{16} cores (excluding isopentanol) is \numrange{0.63}{0.71}, similar to the shallow vectorization's efficiency of \numrange{0.70}{0.78} for \num{4} cores.
